Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-14 data_appendix_all_years.Rmd
created household head and children data frames

```{r import household data 2005}
data_2005 <- read_dta("Raw data/seminar_paper_data/2005_hhsurvey.dta") %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        grade = s3_05b,
        repeated = s3_07,
        income = y_perc1A)

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2005,
         hh_id = as.numeric(hh_id),
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```
```{r export summary table 2005}
export_summary_table(dfSummary(hh_2005))
```

```{r import household data 2006}
data_2006 <- read_dta("Raw data/seminar_paper_data/2006_hhsurvey.dta")  %>% 
  rename(hh_id = Folio,
        assist = s4_08,  
        reason = S4_09, 
        members = mhogar,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s4_01,
        register = s4_04,
        grade = s4_05b,
        repeated = s4_07,
        income = yhogpcf,
        urb_rur = Urb_Rur)

hh_2006 <- data_2006 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, ID01, urb_rur, income) %>% 
  mutate(year = 2006,
         hh_id = as.numeric(hh_id),
         dept = case_when(ID01 == "1" ~ "Chuquisaca",
                          ID01 == "2" ~ "La Paz",
                          ID01 == "3" ~ "Cochabamba",
                          ID01 == "4" ~ "Oruro",
                          ID01 == "5" ~ "Potosi",
                          ID01 == "6" ~ "Tarija",
                          ID01 == "7" ~ "Santa Cruz",
                          ID01 == "8" ~ "Beni",
                          ID01 == "9" ~ "Pando"))
```

@@

```{r import household data 2007}
data_2007 <- read_dta("Raw data/seminar_paper_data/2007_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_10,  
        reason = s4_11, 
        members = mhogar,
        sex = s1_03,
        age = s1_04,
        relation = s1_06,
        literacy = s4_01,
        register = s4_06,
        grade = s4_07b,
        repeated = s4_09,
        income = yhogpcf)

hh_2007 <- data_2007 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2007,
        hh_id = as.numeric(hh_id),
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```

@@

hh_2011 <- data_2011 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, grade, repeated, depto, urb_rur, income, school_level) %>% 
  mutate(year = 2011,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```

```{r import household data 2012}
data_2012 <- read_dta("Raw data/seminar_paper_data/2012_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_12,  
        reason = s4_13,
        sex = s1_03,
        age = s1_04,
        relation = s1_08,
        literacy = s4_01,
        register = s4_04,
        grade = s4_05b,
        repeated = s4_11a,
        income = yhogpc,
        school_level = s4_05a,
        urb_rur = area) 
hh_2012 <- data_2012 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, grade, repeated, departamento, urb_rur, income, school_level) %>% 
  mutate(year = 2012,
         dept = case_when(departamento == "1" ~ "Chuquisaca",
                          departamento == "2" ~ "La Paz",
                          departamento == "3" ~ "Cochabamba",
                          departamento == "4" ~ "Oruro",
                          departamento == "5" ~ "Potosi",
                          departamento == "6" ~ "Tarija",
                          departamento == "7" ~ "Santa Cruz",
                          departamento == "8" ~ "Beni",
                          departamento == "9" ~ "Pando"))
```

```{r import household data 2013}
data_2013 <- read_dta("Raw data/seminar_paper_data/2013_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s5_10,  
        reason = s5_11,
        sex = s2_02,
        age = s2_03,
        relation = s2_05,
        literacy = s5_01,
        register = s5_04,
        grade = s5_05b,
        income = yhogpc,
        school_level = s5_05a,
        urb_rur = area) 
hh_2013 <- data_2013 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, grade, id01, urb_rur, income, school_level) %>% 
  mutate(year = 2013,
         dept = case_when(id01 == "1" ~ "Chuquisaca",
                          id01 == "2" ~ "La Paz",
                          id01 == "3" ~ "Cochabamba",
                          id01 == "4" ~ "Oruro",
                          id01 == "5" ~ "Potosi",
                          id01 == "6" ~ "Tarija",
                          id01 == "7" ~ "Santa Cruz",
                          id01 == "8" ~ "Beni",
                          id01 == "9" ~ "Pando"))
```

```{r import household survey 2014}
data_2014 <- read_dta("Raw data/seminar_paper_data/2014_hhsurvey.dta") %>%
  rename(hh_id = folio,
        assist = s5b_10,  
        reason = s5b_11,
        sex = s2a_02,
        age = s2a_03,
        relation = s2a_05,
        literacy = s5a_01,
        register = s5a_04,
        grade = s5a_05a,
        income = yhogpc,
        school_level = s5a_05,
        urb_rur = URBRUR) 
hh_2014 <- data_2014 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, grade, DEPTO, urb_rur, income, school_level) %>% 
  mutate(year = 2014,
         dept = case_when(DEPTO == "1" ~ "Chuquisaca",
                          DEPTO == "2" ~ "La Paz",
                          DEPTO == "3" ~ "Cochabamba",
                          DEPTO == "4" ~ "Oruro",
                          DEPTO == "5" ~ "Potosi",
                          DEPTO == "6" ~ "Tarija",
                          DEPTO == "7" ~ "Santa Cruz",
                          DEPTO == "8" ~ "Beni",
                          DEPTO == "9" ~ "Pando"))
```

```{r import household survey 2015}
data_2015 <- read_dta("Raw data/seminar_paper_data/2015_hhsurvey.dta") %>%
   rename(hh_id = folio,
        assist = s5b_10,  
        reason = s5b_11,
        sex = s2a_02,
        age = s2a_03,
        relation = s2a_05,
        literacy = s5a_1,
        register = s5a_4,
        grade = s5a_5b,
        income = yhogpc,
        school_level = s5a_5a,
        urb_rur = area) 
hh_2015 <- data_2015 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, grade, departamento, urb_rur, income, school_level) %>% 
  mutate(year = 2015,
         dept = case_when(departamento == "1" ~ "Chuquisaca",
                          departamento == "2" ~ "La Paz",
                          departamento == "3" ~ "Cochabamba",
                          departamento == "4" ~ "Oruro",
                          departamento == "5" ~ "Potosi",
                          departamento == "6" ~ "Tarija",
                          departamento == "7" ~ "Santa Cruz",
                          departamento == "8" ~ "Beni",
                          departamento == "9" ~ "Pando"))

@@

```{r import household data 2016}
data_2016 <- read_dta("Raw data/seminar_paper_data/2016_hhsurvey.dta")  %>%
   rename(hh_id = folio,
        assist = s05b_10,  
        reason = s05b_11,
        sex = s02a_02,
        age = s02a_03,
        relation = s02a_05,
        literacy = s05a_01,
        register = s05a_05,
        grade = s05a_06b,
        income = yhogpc,
        school_level = s05a_06a,
        urb_rur = area) 
hh_2016 <- data_2016 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, grade, depto, urb_rur, income, school_level) %>% 
  mutate(year = 2016,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))

```{r import household survey 2017}
data_2017 <- read_dta("Raw data/seminar_paper_data/2017_hhsurvey.dta")  %>%
  rename(hh_id = folio,
        assist = s05b_10,  
        reason = s05b_11,
        sex = s02a_02,
        age = s02a_03,
        relation = s02a_05,
        literacy = s05a_01,
        register = s05a_05,
        grade = s05a_06b,
        income = yhogpc,
        school_level = s05a_06a,
        urb_rur = area) 
hh_2017 <- data_2017 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, grade, depto, urb_rur, income, school_level) %>% 
  mutate(year = 2017,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))

```{r import household data 2018}
data_2018 <- read_dta("Raw data/seminar_paper_data/2018_hhsurvey.dta")  %>%
  rename(hh_id = folio,
        assist = s05b_10,  
        reason = s05b_11,
        sex = s02a_02,
        age = s02a_03,
        relation = s02a_05,
        literacy = s05a_01,
        register = s05a_05,
        grade = s05a_06c,
        income = yhogpc,
        school_level = s05a_06a,
        urb_rur = area) 
hh_2018 <- data_2018 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, grade, depto, urb_rur, income, school_level) %>% 
  mutate(year = 2018,
         hh_id = as.numeric(hh_id),
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```

```{r merge household datasets}
```

{r import household survey 2008}
data_2008 <- read_dta("Raw data/seminar_paper_data/2008_hhsurvey.dta")  %>% 
  rename(hh_id = FOLIO,
        assist = S4_13,  
        reason = S4_14, 
        members = MHOGAR,
        sex = S1_03,
        age = S1_04,
        relation = S1_06,
        literacy = S4_01,
        register = S4_05,
        grade = S4_06B,
        repeated = S4_12,
        income = YHOGPCF)

hh_2008 <- data_2008 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2008,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```
## Flood data
**Citation:** GeoSinager. (2016). Mapa Recurrencias de Inundaciones Gestiones 2002-2012. [CSV file]. Retrieved from http://geosinager.defensacivil.gob.bo/maps/226

@@

export_summary_table(dfSummary(flood_summary))
```

## Drought data
**Citation:** GeoSinager. (2016). Mapa Recurrencias de Sequias Gestiones 2002-2012. [CSV file]. Retrieved from http://geosinager.defensacivil.gob.bo/maps/225

@@

``` {r merging datasets}
total_2005 <- hh_2005 %>% 
  left_join(flood_summary) %>%
  left_join(drought_summary)

export_summary_table(dfSummary(total_2005))

save("total_2005", file = "processed_data/analysis_data.RData")

@@

>>>>

```{r import household data 2005}
data_2005 <- read_dta("Raw data/seminar_paper_data/2005_hhsurvey.dta") %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        school_level = s3_05a,
        grade = s3_05b,
        repeated = s3_07,
        income = y_perc1A)

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2005,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
         reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))

```{r export summary table 2005}
export_summary_table(dfSummary(hh_2005))

```{r import household data 2006}
data_2006 <- read_dta("Raw data/seminar_paper_data/2006_hhsurvey.dta")  %>% 
  rename(hh_id = Folio,
        assist = s4_08,  
        reason = S4_09, 
        members = mhogar,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s4_01,
        register = s4_04,
        school_level = s4_05a,
        grade = s4_05b,
        repeated = s4_07,
        income = yhogpcf,
        urb_rur = Urb_Rur,
        depto = ID01)

hh_2006 <- data_2006 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2006,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

@@

```{r import household data 2007}
data_2007 <- read_dta("Raw data/seminar_paper_data/2007_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_10,  
        reason = s4_11, 
        members = mhogar,
        sex = s1_03,
        age = s1_04,
        relation = s1_06,
        literacy = s4_01,
        register = s4_06,
        school_level = s4_07a,
        grade = s4_07b,
        repeated = s4_09,
        income = yhogpcf)

hh_2007 <- data_2007 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2007,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

@@

hh_2011 <- data_2011 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2011,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

```{r household data 2012}
data_2012 <- read_dta("Raw data/seminar_paper_data/2012_hhsurvey.dta")  %>% 
  rename(hh_id = folio,
        assist = s4_12,  
        reason = s4_13,
        sex = s1_03,
        age = s1_04,
        relation = s1_08,
        literacy = s4_01,
        register = s4_04,
        grade = s4_05b,
        repeated = s4_11a,
        income = yhogpc,
        school_level = s4_05a,
        urb_rur = area,
        depto = departamento)

hh_2012 <- data_2012 %>% 
  select(hh_id, assist, reason, sex, age,
         relation, literacy, register, school_level, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2012,
         dept = case_when(depto== "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
           reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work', 
                            reason == 4 ~ 'sickness/accident/disability', 
                            reason == 5 ~ 'distance',
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested', 
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

```{r combine household datasets}
all_years <- hh_2005 %>% 
  #bind_rows(hh_2005, hh_2006, hh_2007, hh_2011, hh_2012)
  rbind(hh_2005, hh_2006)

@@

## Flood data
**Citation:** GeoSinager. (2016). Mapa Recurrencias de Inundaciones Gestiones 2002-2012. [CSV file]. Retrieved from http://geosinager.defensacivil.gob.bo/maps/226

@@

export_summary_table(dfSummary(flood_summary))
```
## Drought data
**Citation:** GeoSinager. (2016). Mapa Recurrencias de Sequias Gestiones 2002-2012. [CSV file]. Retrieved from http://geosinager.defensacivil.gob.bo/maps/225

@@

``` {r merging datasets}
total_data<- all_years %>% 
  left_join(flood_summary) %>%
  left_join(drought_summary)

export_summary_table(dfSummary(total_data))

save("total_data", file = "processed_data/analysis_data.RData")

@@

```{r creating head of household subset}

hh_head <- subset(total_data, relation == 1, select = c("hh_id", "sex", "age", "literacy", "dept", "urb_rur", "income", "year"))

```{r creating children subset}

children <- subset(total_data, age < 18 & age > 4, select = c("hh_id", "age", "sex", "literacy", "dept", "urb_rur", "income", "assist", "reason", "register", "school_level", "grade", "repeated", "floods", "droughts"))
